---
title: "RMARKDOWN AND LEAFLET"
author: "Oluwadare, Margaret"
date: "9/17/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
In this work we are presenting some advantages of using Rmarkdown and leaflet in working with maps. This gives a comfortable alternatives to the traditional softwares that are used.

```{r Loading packages, echo=TRUE}
library(knitr)
library(maps)
library(leaflet)
library(dplyr)
```

The following accompanying codes produces maps of key places in Nigeria.

```{r Key places in Nigeria, echo=TRUE}
olu <- leaflet() %>%
   addTiles() %>%  # Add default OpenStreetMap map tiles
  addMarkers(lat=4.982873, lng = 8.334503, popup = "THE CITY OF CALABAR, Calabar") %>%
  addMarkers(lat = 6.3858,lng = 9.3745,popup ="Obudu ranch mountain resort,Obudu") %>%
  addMarkers(lat = 9.0833,lng = 7.5361, popup="ASO ROCK, ABJ") %>%
  addMarkers(lat = 7.7833333333,lng = 10.00000000, popup ="RIVER BENUE, MARKURDI") %>%
  addMarkers(lat=7.4273,lng=4.9091, popup="IPETU-IJESA, OSUN") %>%
  addMarkers(lat=4.8177,lng=8.02593, popup="NSIT ATAI, AKWA IBOM STATE") 
  

olu  
```
Also taking a look at the famous river Niger.

```{r River niger, echo=TRUE}
ade<- leaflet() %>%
   addTiles() %>%  
   addMarkers(lat = 13.8601, lng = -3.333328, popup = "RIVER NIGER")
   
ade
```
CONCLUSION
----------
Using the Rmarkdown and leaflet to present maps makes less stressful and does not require full knowledge of the usual map applications.
